% $Id$

This section describes how to use the Java Management Extention API along with JacORB to
instrument both the orb and application that use JacORB.

\section{MX4J and JMX over IIOP}

This section describes how to instrument a JacORB application using the MX4J JMX implementation.
MX4J is an open source JMX implementation available at http://mx4j.sourceforge.net. This section
also shows how to use JMX over IIOP. This allows JMX to use an existing JacORB ORB for RMI
communications and the JacORB Naming Service to register you JMX MBeanServer.

To setup the JVM environment, three system defines are neccessary:

\begin{scriptsize}
\begin{verbatim}
-Djava.naming.factory.initial=com.sun.jndi.cosnaming.CNCtxFactory
-Djava.naming.provider.url=corbaloc:iiop:localhost:9101/StandardNS/NameServer-POA/_root
-Djavax.rmi.CORBA.PortableRemoteObjectClass=org.jacorb.orb.rmi.PortableRemoteObjectDelegateImpl
\end{verbatim}
\end{scriptsize}

The first system property tells the Java JNDI subsystem to use the CORBA Naming Service for its
naming repository. The second property is a pointer to the JacORB Naming Service instance. The
third property tells the Java Remote object system to use JacORB's Portable Remote Object implementation. This is required so that JacORB can associate an RMI object with a CORBA object on one of its POAs.

The sample code for creating a MBeanServer is shown below

\begin{scriptsize}
\begin{verbatim}
// The MBeanServer to which the JMXConnectorServer will be registered in
jmxServer = MBeanServerFactory.createMBeanServer();
            
// The address of the connector
HashMap environment = new HashMap();
org.jacorb.orb.rmi.PortableRemoteObjectDelegateImpl.setORB(orb);
JMXServiceURL address = new JMXServiceURL("service:jmx:iiop://localhost/jndi/jmxSnmpTrapNotify");
JMXConnectorServer cntorServer = JMXConnectorServerFactory.newJMXConnectorServer(address,                                             environment, jmxServer);
            
// Add MBeans
jmxServer.registerMBean(trapReceiver, new ObjectName("TrapReceiver:counts=default"));
            
// Start the JMXConnectorServer
cntorServer.start();
\end{verbatim}
\end{scriptsize}

The first line creates the MBeanServer. 
The next 4 lines creates the remote JMX connection. The "`setORB()"' call assignes a previously
initialized ORB to the Remote Object delegate. All RMI over IIOP communications will occure
via this ORB. The "`address"' is the name of the MBeanServer as known in the Naming service.
The portion after "`/jndi/"' is the Naming Service name.
The next line registers a MBean with the MBeanServer.
The last line starts the MBeanServer.

A JMX console may then be used to monitor the JacORB application. For example, MC4J (http://mc4j.sourceforge.net) may be used. When setting up a mc4j connection, use the connection type JSR160 and set the server URL to the name as registered in the JacORB naming service, such as 
"`service:jmx:iiop://localhost/jndi/jmxSnmpTrapNotify"'.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../ProgrammingGuide"
%%% End: 
