
\section{Maven Central}

JacORB is now available in Maven Central under the following GAVs (Group-Artifact-Version):

\begin{itemize}
\item Group: \texttt{org.jacorb}
\item Artifacts:
  \begin{itemize}
    \item \texttt{jacorb}
    \item \texttt{jacorb-omgapi}
    \item \texttt{jacorb-idl-compiler}
    \item \texttt{jacorb-parent}
    \item \texttt{jacorb-services}
  \end{itemize}
\end{itemize}

The current version is \JacORBVersion.


\section{Maven Demo}

An example is supplied in \texttt{<install>/demo/maven} in order to demonstrate the use of Maven to download the JacORB artifacts, use the IDL compiler plugin and finally executing the resulting client/server. The following will describe the steps in detail.

\subsubsection{IDL Compiler}
Before the main source files can be compiled the IDL must be generated. To do this an external plugin is used. The GAV for this plugin is:
\begin{itemize}
\item \texttt{org.codehaus.mojo.idlj-maven-plugin:1.2.1}
\end{itemize}

and is documented here \href{http://mojo.codehaus.org/idlj-maven-plugin}{http://mojo.codehaus.org/idlj-maven-plugin}. Note to correctly configure the plugin the type of IDL compiler must be configured and a dependency upon the correct version of the JacORB IDL compiler added e.g.
\begin{verbatim}
           <plugin>
                ...

                <configuration>
                    <compiler>jacorb</compiler>
                </configuration>
                <dependencies>
                    <dependency>
                        <groupId>org.jacorb</groupId>
                        <artifactId>jacorb-idl-compiler</artifactId>
                        <version>${version.jacorb}</version>
                        <scope>compile</scope>
                    </dependency>
                </dependencies>
            </plugin>
\end{verbatim}

\subsubsection{Compiling}
Assuming the correct JacORB dependency has been added to the Maven POM the default Maven lifecycle will build both
the generated sources and the supplied sources during the 'compile' phase.
\begin{verbatim}
    <dependencies>
        <dependency>
            <groupId>org.jacorb</groupId>
            <artifactId>jacorb</artifactId>
            <version>${version.jacorb}</version>
        </dependency>
    </dependencies>
\end{verbatim}

\paragraph{Note:}
The JacORB core and services have a transient dependency on the OMG API stubs:

\begin{verbatim}
    <dependencies>
        <dependency>
            <groupId>org.jacorb</groupId>
            <artifactId>jacorb-omgapi</artifactId>
            <version>${version.jacorb}</version>
        </dependency>
    </dependencies>
\end{verbatim}

This may need to be explicitly added to the compile / exec Xbootclasspath's if
you wish to use JacORB's OMG stubs.

\subsubsection{Running}
By default JacORB core and services depend upon slf4j-api. To configure the default JDK logging
add the following dependency.
\begin{verbatim}
    <dependencies>
      <dependency>
        <groupId>org.slf4j</groupId>
        <artifactId>slf4j-jdk14</artifactId>
      </dependency>
    </dependencies>
\end{verbatim}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../ProgrammingGuide"
%%% End:
