
JacORB offers a certain level of control over connections and timeouts. You
can
\begin{itemize}
\item set connection idle timeouts.
\item set request timing.
\item set the maximum number of accepted TCP/IP connections on the server.
\end{itemize}

\section{Timeouts}
\label{connection_timeouts}
Connection idle timeouts can be set individually for the client and the
server. They control how long an idle connection, i.e.~a connection that has
no pending replies, will stay open. The corresponding properties are {\tt
  jacorb.connection.client.idle\_timeout} and {\tt
  jacorb.connection.server.timeout} and take their values as milliseconds. If
not set, connections will stay open indefinitely (or until the OS decides to
close them).

\emph{Request timing} controls how long an individual request may take to
complete.  The programmer can specify this using QoS policies,
discussed in chapter \ref{ch:qos}.

\section{Connection Management}
\label{connection_management}

When a client wants to invoke a remote object, it needs to send the request
over a connection to the server. If the connection isn't present, it has to be
created. In JacORB, this will only happen once for every combination of host
name and port. Once the connection is established, all requests and replies
between client and server will use the same connection. This saves resources
while adding a thin layer of necessary synchronization, and is the recommended
approach of the OMG. Occasionally people have requested to allow for multiple
connections to the same server, but nobody has yet presented a good argument
that more connections would speed up things considerably.

On the server side, the property {\tt
  jacorb.connection.max\_server\_connection} allows to set the maximum number
of TCP/IP connections that will be listened on for requests. When using a
network sniffer or tools like netstat, more inbound TCP/IP connections than
the configured number may be displayed. This is for the following reason:
Whenever the connection limit is reached, JacORB tries to close existing idle
connections (see the subsection below). This is done on the thread
that accepts the new connections, so JacORB will not actively accept more
connections. However, the ServerSocket is initialized with a backlog of 20.
This means that 20 more connections will be quasi-accepted by the OS. Only the
21st will be rejected right away.

\subsection{Basics and Design}
\label{connection_management_basics}
Whenever there is the need to close an existing connection because of the
connection limit, the question arises on which of the connection to close. To
allow for maximum flexibility, JacORB provides the interface {\tt
  SelectionStrategy} that allows for a custom way to select a connection to
close. Because selecting a connection usually requires some sort of
statistical data about it, the interface {\tt
  StatisticsProvider} allows to implement a class that collects statistical
data.

\begin{small}
\begin{verbatim}
package org.jacorb.orb.giop;

public interface SelectionStrategy
{
    public ServerGIOPConnection
        selectForClose( java.util.List connections );
}

public interface StatisticsProvider
{
    public void messageChunkSent( int size );
    public void flushed();
    public void messageReceived( int size );
}
\end{verbatim}
\end{small}

The interface {\tt SelectionStrategy} has only the single method of {\tt
  selectForClose()}. This is called by the class {\tt GIOPConnectionManager}
when a connection needs to be closed. The argument is a {\tt List} containing
objects of type {\tt ServerGIOPConnection}. The call itself is synchronized in
the {\tt GIOPConnectionManager}, so no additional synchronization has to be
done by the implementor of {\tt SelectionStrategy}. When examining the
connections, the strategy can get hold of the {\tt StatisticsProvider} via the
method {\tt getStatisticsProvider()} of the class {\tt GIOPConnection}. The
strategy implementor should take care only to return idle connections. While
the connection state is checked anyway while closing (it may have changed in
the meantime), it seems to be more efficient to avoid cycling through the
connections. When no suitable connection is available, the strategy may
return {\tt null}. The {\tt GIOPConnectionManager} will then wait for a
configurable time, and try again. This goes on until a connection can be
closed.

The interface {\tt StatisticsProvider} is used to collect statistical data
about a connection and provide it to the {\tt SelectionStrategy}.  Because the
nature of this data may vary, there is no standard access to the data via the
interface. Therefore, {\tt StatisticsProvider} and {\tt SelectionStrategy}
usually need to be implemented together. Whenever a new connection is
created\footnote{Currently, connection management is only implemented for the
server side. Therefore, only accepted {\tt ServerGIOPConnections}s will get a
{\tt StatisticsProvider}}, a new {\tt StatisticsProvider} object is
instanciated and stored with the {\tt GIOPConnection}\footnote{This is
actually only done when a {\tt StatisticsProvider} is configured}.
The {\tt StatisticsProvider} interface is oriented along the mode of use of the {\tt
GIOPConnection}. For efficiency reasons, messages are not sent as one big byte
array. Instead, they are sent piecewise over the wire. When such a chunk is
sent, the method {\tt messageChunkSent(int size)} will be called. After the
message has been completely sent, method {\tt flush()} is called. This whole
process is synchronized, so all consecutive {\tt messageChunkSent}s until a
{\tt flush()} form a single message. Therefore, no synchronization on this
level is necessary. However, access to gathered statistical data by the {\tt
SelectionStrategy} is concurrent, so care has to be taken. Receiving messages
is done only on the whole, so there exists only one method, {\tt
messageReceived(int size)}, to notify the {\tt StatisticsProvider} of such an
event.


JacORB comes with two pre-implemented strategies: least frequently used and
least recently used. LFU and LRU are implemented by the classes {\tt
  org.jacorb.orb.giop.L[F|R]USelection\-StrategyImpl} and {\tt
  org.jacorb.orb.giop. L[F|R]U\-Statistics\-ProviderImpl}.

\subsection{Configuration}
\label{connection_management_config}
To configure connection management, the following properties are provided:
\begin{description}
\item {\tt jacorb.connection.max\_server\_connections} This property sets the
  maximum number of TCP/IP connections that will be listened on by the
  server--side ORB.
\item {\tt jacorb.connection.wait\_for\_idle\_interval} This property sets the
  interval to wait until the next try is made to find an idle connection to
  close. Value is in microseconds.
\item {\tt jacorb.connection.selection\_strategy\_class} This property sets
  the {\tt Selection\-Strategy}.
\item {\tt jacorb.connection.statistics\_provider\_class} This property sets
  the {\tt Statistics\-Provider}.
\item {\tt jacorb.connection.delay\_close} If turned on, JacORB will delay
  closing of TCP/IP connections to avoid certain situations, where message
  loss can occur. See also section \ref{connection_management_limitations}.
\end{description}

\subsection{Limitations}
\label{connection_management_limitations}
When trying to close a connection, it is first checked that the connection is
idle, i.e.~has no pending messages.  If this is the case, a GIOP
CloseConnection message is sent, and the TCP/IP connection is closed. Under
high load, this can lead to the following situation:

\begin{enumerate}
\item Server sends the CloseConnection message.
\item Server closes the TCP/IP connection.
\item The client sends a new request into the connection, because it hasn't
  yet read and acted on the CloseConnection message.
\item The server--side OS will send a TCP RST, which cancels out the
  CloseConnection message.
\item The client finds the connection closed and must consider the request lost.
\end{enumerate}

To get by this situation, JacORB takes the following approach. Instead
of closing the connection right after sending the CloseConnection
message, we delay closing and wait for the client to close the
connection. This behaviour is turned off by default, but can be
enabled by setting the property {\tt jacorb.connection.delay\_close}
to ``yes''. When non-JacORB clients are used care has to be taken that
these ORBs do actively close the connection upon receiving a
CloseConnection message.


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../ProgrammingGuide"
%%% End:
